Rule learning for verification from temporal data

### 2016-09-04 Travis/secs/intro.tex
newintro

Machine learning can be a powerful tool for for software analysis and verification \cite{lau2000version,Santolucito2016,gehrpsi,garg2014ice}.
However, many popular machine learning algorithms, such as neural nets and n-gram models, are not designed to provide simple justifications for their classification results.
While effective in practice, the lack of justification for the results limits the applicability.
In the case of error detection, the system should not only report which files have errors, but also identify the errors.
Version space learning is a learning strategy for logical constraint classification~\cite{mitchell82}, which can be used to easily provide clear error messages.

@@

Extensions to version space learning have been used in various software analysis techniques, such as programming-by-example \cite{lau2000version}, invariant synthesis \cite{garg2014ice}, and error detection \cite{Santolucito2016}.
In previous work we used machine learning to verify configuration files by automatically learning a language model from a set of correct examples~\cite{Santolucito2016}.
We give a formal definition of the algorithm in terms of version space learning to show how clear error messages can be produced with this technique.
%and show that the results are garunteed to be complete.

%Although the results are complete, the approach used previously produces a high false positive rate.
Although the error messages are clear, the approach used previously produces a high false positive rate (marks correct files as incorrect).
To decrease this, we propose an extention to the algorithm to handle sets of both incorrect and correct examples, which have a partial order.
A partial order is common in learning sets for machine learning program analysis, as code does not exist in isolation, but changes over time with development.
Any analysis that makes use of code from a version control system like Github will have this property.
We predict this algorithm has the potential to significantly reduce the false positive rate.
%A learning algorithm that uses the temporal structure of code to create sound classification with a low false positive rate can be used in at least the above listed software analysis techniques.

>>>>

Machine learing has been used in various software analysis techniques, such as programming-by-example \cite{lau2000version}, invariant synthesis \cite{garg2014ice}, and error detection \cite{Santolucito2016}.
However, many popular machine learning algorithms, such as neural nets and n-gram models, are not designed to provide simple justifications for their classification results.
While effective in practice, the lack of justification for the results limits the applicability to software analysis, where justification is critical.
In the case of error detection, the system should not only report which files have errors, but also locate the errors.
Version space learning is a learning strategy for logical constraint classification~\cite{mitchell82}, which can be used to easily provide clear error messages.

@@

In our previous work we used version space learning to verify configuration files from a set of correct examples~\cite{Santolucito2016}.
The tool, ConfigC, takes examples of correct files, builds a language model, which is then used to check is new configuration files adhear to those rules.
If a file is incorrect, the tool will identify the location of error, what is incorrect.
For example, ConfigC might output \texttt{Ordering Error: Expected "extension mysql.so" before "extension recode.so"}.
We describe here this algorithm in terms of version space learning to show how clear error messages are produced with this technique.
%and show that the results are garunteed to be complete.

%Although the results are complete, the approach used previously produces a high false positive rate.
Although the error messages are clear, the approach used previously produces a high false positive rate (marks correct files as incorrect).
To decrease this, in this paper we propose an extention to the algorithm to handle sets of both incorrect and correct examples.
We also use a commonly avaible, but underutilized structure of learning sets for machine learning for software analysis.
Because most code does not exist in isolation, but changes over time with development, examples for a learning set can also leverage this temporal structure. 
This structure is simply a partial order, and any analysis that makes use of code from a version control system like Github will have this property.
We predict this algorithm has the potential to significantly reduce the false positive rate.
%A learning algorithm that uses the temporal structure of code to create sound classification with a low false positive rate can be used in at least the above listed software analysis techniques.
